---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Emily Dorn"
date: "8/29/2019"
output: 
  html_document: 
    fig_height: 6
    fig_width: 8
    highlight: zenburn
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

There are 1846 rows and 3 columns. The variables included are dataset, x, and y.

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The shape of the plot is a dinosaur.

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

The correlation coefficient is -0.0645.
### Exercise 3

```{r plot-star}
star_data <- datasaurus_dozen %>%
   filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
   geom_point()
```

Take the dinsaurus_dozen data frame and then filter it for observations where data == "dino".

Star data is getting mapped to the plot.

```{r cor-star}
star_data %>%
   summarize(r = cor(x, y))
```

Start with the star_data, then calculate a summary statistic that we call r as the correlation between x and y.

There is little difference between the dino data's correlation (-0.0645) and the star data's correlation (-0.0630). Both have poor negative correlations that differ in 0.005.

### Exercise 4

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
   filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
   geom_point()
```

Pulling the circle dataset from datasaurus_dozen.

Plotting the circle dataset from datasaurus_dozen.

```{r cor-circle}
circle_data %>%
   summarize(r = cor(x, y))
```

Finding the correlation in the circle dataset.

The correlation in the circle dataset (-0.0683) is slightly better than the correlation in the dino dataset, but not by much. The difference is so minute that it does not matter much. 


### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)

```{r plot-all}
ggplot(data = datasaurus_dozen, aes(x=x, y=y, color = dataset)) + 
   geom_point() + 
   facet_wrap(~ dataset, ncol = 3) +
   theme(legend.position = "none")
```

In the ggplot function, the color = dataset code command assigns each dataset a unique color. The ncol option inside the facet_wrap command organizes the plots into 3 columns. Finally, the theme(legend.position = "none") tells R to not include a legend when creating the plots.

```{r}
datasaurus_dozen %>%
   group_by(dataset) %>%
   summarize(r = cor(x,y)) %>%
   print(13)
```
